Tree size, exposure, and hydraulic traits interactively shape drought response in a temperate broadleaf forest

### 2019-07-24 manuscript/03-methods.Rmd
Updated references and methods

`diam_1999 = dbh2008 - 2*(bark.depth2008) - 2*(sum(ring.width1999:ring.width2008)) + 2*(bark.depth_1999)`  (**clean up this equation--put a generic year instead of 1999, use sum symbol, etc.**)

@@

To determine focus drought years, we used the pointRes package [@R-pointRes] in R (version 3.5.2) to determine resilience metrics. Specifically, we calculated pointer years (main drought years) if >50% of the cored trees experienced <30% growth in a year compared to the previous 5 years. The top 6 pointer years were compared with PDSI (Palmer Drought Severity Index) values for the region, obtained from NOAA. Based on this comparison, we then took the top three pointer years of 1964-1966 (resistance metric averaged due to a single, prolonged drought), 1977, and 1999. [**This needs work. It's very complex to describe what you did, and in retrospect not well-aligned with our current analysis. It would be much more straightforward to simply combine ALL cores in the pointRes package to identify potential pointer years. Is this a lot of work? In any case, we should find a way to present this analysis in one paragraph (no tables!) of main body text. If you need to stick with species/crown position-level analysis, any tables and detailed description should go in SI**]

>>>>

$$
diamYEAR = dbh2008 - 2*(bark.depth2008) - 2*\Sigma(ring.width1999:ring.width2008) + 2*(bark.depth_YEAR)
$$

@@

To accurately understand climate sensitivity, this study used a specific definition of drought, which is not a common practice [@slette_how_2019]. We used the pointRes package [@R-pointRes] in R (version 3.5.3) to determine drought periods based on trees' drought resistance, which is defined by [@lloret_components_2011] as the ratio between the performance during and before the disturbance. Candidate drought years were defined if >50% of the cored trees experienced <30% growth in a year compared to the previous 5 years. These were then cross-validated with the regional Palmer Drought Severity Index (PDSI) values for each year, which yielded a set of three periods that were consistently shown as drought: 1964-1966, 1977, and 1999.

[**We should find a way to present this analysis in one paragraph (no tables!) of main body text. If you need to stick with species/crown position-level analysis, any tables and detailed description should go in SI**]
